---
title: "Midcourse Notebook"
output: html_notebook
---

# Import the libraries that we need to make the stuff work.

```{r Library Imports}
library(ggplot2)
library(tidyr)
library(tidyverse)
library(dplyr)
library(readr)
library(sf)
library(stringr)
library(data.table)
library(janitor)
```

# Import the Data as CSV with readr

```{r .csv imports}
district_2018 <- read_csv("data/district/district_2018.csv")
district_2019 <- read_csv("data/district/district_2019.csv")
district_2021 <- read_csv("data/district/district_2021.csv")
district_2022 <- read_csv("data/district/district_2022.csv")
```

# Something kinda funky is going on. There's a differeing amount of variable data for each column.

```{r Combined all datasets into one}
EOC_Pre <- bind_rows(district_2018, district_2019, district_2021) %>% 
  rename(n_met_expectations = n_on_track, 
         pct_met_expectations = pct_on_track,
         n_exceeded_expectations = n_mastered,
         pct_exceeded_expectations = pct_mastered,
         student_group = subgroup)
EOC_Merged <- bind_rows(EOC_Pre, district_2022)
```

# Look at it with the janitor. It appears as if some of the criteria for mastery have changed over the years. I reached out to DOE, They explained which are equivalent.

```{r groundskeeper_willie}
groundskeeper_willie <- janitor::compare_df_cols(district_2018, district_2019, district_2021, district_2022)
groundskeeper_willie
```

# Merging Columns
```{r}
zTestUnite <- 
  EOC %>% unite(test, n_on_track,n_met_expectations)
```

# Dropping Unneeded Columns

```{r Column remove}
EOC_Drop <- EOC %>% 
  select(-c(participation_rate, student_group, enrolled, tested, valid_tests))
```

#Describing columns

```{r Categorical Variables}
dist_assess <- EOC %>% distinct(grade, subject, test)
dist_assess <- EOC %>% distinct(grade, subject, test)

```
