---
title: "Midcourse Notebook"
output: html_notebook
---
# Import the libraries that we need to make the stuff work.
```{r Library Imports}
library(ggplot2)
library(tidyr)
library(tidyverse)
library(dplyr)
library(readr)
library(sf)
library(stringr)
library(data.table)
library(janitor)
library(data.table)
```

# Import the Data as CSV with readr
```{r .csv imports}
district_2018 <- read_csv("data/district/district_2018.csv")
district_2019 <- read_csv("data/district/district_2019.csv")
district_2021 <- read_csv("data/district/district_2021.csv")
district_2022 <- read_csv("data/district/district_2022.csv")
```

# Something kinda funky is going on.  There's a differeing amount of variable data for each column.
```{r Combined all datasets into one}
EOC <- bind_rows(district_2018, district_2019, district_2021, district_2022)
```
 
# Look at it with the janitor.  It appears as if some of the criteria for mastery have changed over the years.
Ill have to do some research to see if they are equivalent (Hopefully!)
```{r}
groundskeeper_willie <- janitor::compare_df_cols(district_2018, district_2019, district_2021, district_2022)
groundskeeper_willie
```

# Dropping Unneeded Columns
```{r Column remove}
EOC_Drop <- EOC %>% 
  select(-c(participation_rate, student_group, enrolled, tested, valid_tests))
```

#Describing columns
```{r Categorical Variables}
dist_assess <- EOC %>% distinct(grade, subject, test)

```

