---
title: "Midcourse Notebook"
output: html_notebook
---

# Import the libraries that we need to make the stuff work.

```{r Library Imports}
library(ggplot2)
library(tidyr)
library(tidyverse)
library(dplyr)
library(readr)
library(sf)
library(stringr)
library(data.table)
library(janitor)
library(CGPfunctions)
```

# Import the Data as CSV with readr

```{r .csv imports}
district_2018 <- read_csv("data/district/district_2018.csv")
district_2019 <- read_csv("data/district/district_2019.csv")
district_2021 <- read_csv("data/district/district_2021.csv")
district_2022 <- read_csv("data/district/district_2022.csv")
```

# Look at it with the janitor. It appears as if some of the criteria for mastery have changed over the years.

```{r groundskeeper_willie}
groundskeeper_willie <- janitor::compare_df_cols(district_2018, district_2019, district_2021, district_2022)
groundskeeper_willie
```

# I reached out to DOE, They explained which columns are equivalent.

```{r Combined all datasets into one}
assessments_pre <- bind_rows(district_2018, district_2019, district_2021) %>% 
  rename(n_met_expectations = n_on_track, 
         pct_met_expectations = pct_on_track,
         n_exceeded_expectations = n_mastered,
         pct_exceeded_expectations = pct_mastered,
         student_group = subgroup,
         pct_met_exceeded = pct_on_mastered)
assessments_merged <- bind_rows(assessments_pre, district_2022)
```

# Dropping Unneeded Columns
```{r Column remove}
assessments_dropped <- assessments_merged %>% 
  select(-c( n_below, n_approaching, n_met_expectations, n_exceeded_expectations, participation_rate, enrolled, tested, valid_tests))
```

# Removing Student Demographic information
```{r filtered for all students in all grades}
assessments <- assessments_dropped %>% 
  filter(student_group == "All Students", grade == "All Grades") %>% 
  select(-c(grade, student_group)) 
```

# Describing columns
```{r Categorical Variables}
systems <- assessments %>% distinct(system_name)
test_subjects <- assessments %>% distinct(test, subject)
```

# Filter Dataset for suppressed scores
```{r All Suppressed Scores}
suppression_all <- assessments %>% 
  filter(pct_below %in% c("*", "**"), 
        pct_approaching %in% c("*", "**"),
        pct_met_expectations %in% c("*", "**"),
        pct_exceeded_expectations %in% c("*", "**")) %>%
  group_by(system_name, test)
```

# Looking for Assessments with high suppression rates for rates of score reporting. If one subject is suppressed, all will be.
```{r Suppressed completion rate}
suppression_completion <- suppression_all %>% 
  filter(pct_met_exceeded %in% c("*")) %>% 
  transmute(test, subject) %>% 
  group_by(subject, .groups = test) %>% 
  summarise(count = n())
```

# Suppression for Proficiency Outliess
```{r Suppressed Outliers x<1% or x>99%}
suppression_outliers <- suppression_all %>% 
  filter(pct_below %in% c("**")) %>% 
  #transmute(system_name) %>% 
  group_by(system_name, ) %>% 
  summarise(count = n())
```

# Warning: Coercing the assessments!
```{r}
assessments <- assessments %>%  
  mutate(pct_met_exceeded = as.numeric(pct_met_exceeded), 
         pct_below = as.numeric(pct_below), 
         pct_approaching = as.numeric(pct_approaching),
         pct_met_expectations = as.numeric(pct_met_expectations),
         pct_exceeded_expectations = as.numeric(pct_exceeded_expectations))
```
# Visualization Variables
```{r Input Select }
input_system_name <- 'Davidson County'
input_test <- 'EOC'
input_subject <- 'Geometry'
```

# This is why we pivot
```{r Absolutely not the right way to do this}
assessments %>% 
  filter(system_name == input_system_name, test == input_test, subject == input_subject) %>% 
  ggplot(aes(x=year)) + 
  geom_line(aes(y = pct_below), color = "red") +
  geom_line(aes(y = pct_approaching), color = "orange") +
  geom_line(aes(y = pct_met_expectations), color = "yellow") +
  geom_line(aes(y = pct_exceeded_expectations), color = "green") +
  geom_point(aes(y = pct_below)) +
  geom_point(aes(y = pct_approaching)) +
  geom_point(aes(y = pct_met_expectations)) +
  geom_point(aes(y = pct_exceeded_expectations)) +
  ggtitle(paste(input_system_name, input_test, "Scores for", input_subject)) +
  labs(x ="Year", y = "Percent") +
  theme(legend.position = "top")
```
# One more time with pivot longer!
```{r Line Chart}
assessments %>% 
    filter(system_name == input_system_name, test == input_test, subject == input_subject) %>% 
    pivot_longer(pct_below:pct_approaching:pct_met_expectations:pct_exceeded_expectations:pct_met_exceeded, names_to = 'level', values_to = 'score') %>% 
    ggplot(aes(x=year, y=score, color = level)) + 
  geom_line(aes(y = score)) + 
  geom_point(aes(y = score)) +
  ggtitle(paste(input_system_name, input_test, "Scores for", input_subject)) +
  labs(x ="Year", y = "Percent") +
  geom_text(aes(data = score , label = score), check_overlap = TRUE, nudge_y = 2) +
  theme(legend.position = "top")
```

# Another Graph of disruption
```{r Newgg Slope Graph Covid Disruption}
assessments %>% 
    filter(system_name == input_system_name, test == input_test, subject == input_subject) %>% 
    pivot_longer(pct_below:pct_approaching:pct_met_expectations:pct_exceeded_expectations:pct_met_exceeded, names_to = 'level', values_to = 'score') %>%
  filter(year %in% c("2019", "2021")) %>% 
  mutate(year = as.character(year)) %>%
  newggslopegraph(year, score, level,
                Title = paste(input_system_name, input_test, "Scores for", input_subject),
                SubTitle = "Learning Disrupiton",
                Caption = "Please Work",
                LineThickness = 2)   
```

# Stacked Bar
```{r Stacked Bar Chart}
assessments %>% 
    filter(system_name == input_system_name, test == input_test, subject == input_subject) %>%
  select(-c(pct_met_exceeded)) %>% 
    pivot_longer(pct_below:pct_approaching:pct_met_expectations:pct_exceeded_expectations, names_to = 'level', values_to = 'score') %>%
  ggplot(aes(x=year, y=score, fill = level)) +
  geom_bar(stat = "identity") +
  ggtitle(paste(input_system_name, input_test, "Scores for", input_subject)) +
  labs(x ="Year", y = "Percent") +
  geom_text(aes(data = score , label = score), position = position_stack(vjust = .5), size = 3, color = "black")
```
 # calculated columns
```{r test of lag}
assessments %>% 
  group_by(system_name, test, subject) %>%
  arrange(year) %>% 
  mutate(fun_name = pct_below - lag(pct_below))
```
 
